Low-lying collective excited states in non-integrable pairing models based on stationary-phase approximation to path integral

### 2018-11-06 paper2/draft1-5.tex
revised draft1.5
revised draft1.5 after submission to PRC

\begin{abstract}
For a description of large-amplitude collective motion associated with
nuclear pairing, requantization of time-dependent mean-field dynamics
is performed using the stationary-phase approximation (SPA) to the path
integral.
We overcome the difficulty of the SPA, which is known to be applicable to integrable systems only,
by developing a requantization approach combining the SPA with the adiabatic self-consistent collective coordinate method (ASCC+SPA).
%A disadvantage of the SPA is that it is applicable only to integrable systems.
%We overcome this difficulty by developing a requantization approach
%combining the SPA with the adiabatic
%self-consistent collective coordinate method (ASCC+SPA).
We apply the theoretical framework of the ASCC+SPA to 
multi-level pairing models, which are non-integrable systems,
to study the nuclear pairing dynamics.
The ASCC+SPA gives a reasonable description of low-lying excited $0^+$
states in non-integrable pairing systems.
%\begin{description}
%\item[Background] This part would describe the
%context needed to understand what the paper
%is about.
%\item[Purpose] This part would state the purpose
%of the present paper.
%\item[Method] This part describe the methods
%used in the paper.
%\item[Results] This part would summarize the
%results.
%\item[Conclusions] This part would state the
%conclusions of the paper.
%\end{description}
\end{abstract}

@@

We study the low-lying excited $0^+$ states
in the multi-level pairing model by applying the ASCC+SPA.
The Hamiltonian of the pairing model is given in terms of
the single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{align}
	\hat{H} &= \sum_\alpha \epsilon_\alpha \hat{n}_\alpha - g \sum_{\alpha,\beta} \hat{S}_\alpha^+ \hat{S}_{\beta}^- \nonumber \\
    &= \sum_\alpha\epsilon_\alpha(2\hat{S}_\alpha^0+\Omega_\alpha) - g \hat{S}^+ \hat{S}^{-} ,
\end{align}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{S}=\sum_\alpha \boldsymbol{S}_\alpha$, with
\begin{eqnarray}
        \hat{S}_\alpha^0 &=& \frac{1}{2}\left(\sum_m\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha m}-\Omega_\alpha\right) ,\\
        \hat{S}_\alpha^{+} &=& \sum_{m>0}\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha\overline{m}}^{\dag} ,
\quad   \hat{S}_\alpha^{-} = \hat{S}_\alpha^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_\alpha$ possesses $2\Omega_\alpha$-fold
degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$
and $\Omega_\alpha-1/2$.
The occupation number of each level $\alpha$ is given by
$\hat{n}_\alpha = \sum_m \hat{a}^{\dag}_{j_\alpha m}\hat{a}_{j_\alpha m}
=2\hat{S}_\alpha^0+\Omega_\alpha
$.
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [\hat{S}_\alpha^0,\hat{S}_\beta^{\pm}] = \pm\delta_{\alpha\beta}\hat{S}_{\alpha}^{\pm},
\quad [\hat{S}_{\alpha}^{+},\hat{S}_{\beta}^{-}] = 2\delta_{\alpha\beta}\hat{S}_{\alpha}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is given by
$S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
is the seniority
quantum number, namely the number of unpaired particles at the level $\alpha$.
In the present study, we consider only seniority-zero states with
$\nu=\sum_\alpha \nu_\alpha=0$.
The residual two-body interaction consists of the monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain the exact solutions either by solving the Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

@@

\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.45\textwidth,angle=-90]{N16X3p2trajectory.eps}
 \end{center}
\caption{Classical trajectories satisfying the EBK quantization condition
(\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
%The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
The crosses, solid and dashed lines correspond to the results
of the ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively.
The crosses for the ASCC+SPA trajectories are plotted every ten calculations
($\delta q = 10dq =0.1/\sqrt{\epsilon_2-\epsilon_1}$). 
%For the ASCC+SPA trajectories, we plot the crosses
%every ten(?) points of the calculation,
%namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
}
\label{fig:N16_traj}
\end{figure}
\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2action.eps}
 \end{center}
\caption{Calculated action integrals for the $\ket{0_2^+}$ and $\ket{0_3^+}$ states as functions of time $t$.
The crosses, solid and dashed lines correspond to the ASCC+SPA,
the TDHFB2+SPA, and the TDHFB+SPA, respectively. 
%Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
The action integrals are calculated on each trajectory in Fig. \ref{fig:N16_traj}
from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
}
\label{fig:N16_tau}
\end{figure}
\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2occ.eps}
 \end{center}
\caption{
Occupation probabilities for the $0_2^+$ and $0_3^+$ states.
The horizontal line indicates the $j=(m_2-m_1)/2$ of the quasi-spin basis
in Eq. (\ref{SPA2}).
The vertical bars at each $m_2-m_1$ from left to right
represent $|C_m|^2$ of Eq. (\ref{coef}) in
the ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
respectively.
}
 \label{fig:N16_occ}
\end{figure}

@@

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
 \end{center}
 \caption{Eigenvalues of moving-frame QRPA equation as a function of
the collective coordinate $q^1$, from $N=14$ to $N=24$.
The thick (green) lines are the modes we choose as
the collective coordinate $q^1$,
while the dashed lines correspond to the zero modes ($q^n$).
In each panel, both ends of the horizontal axis corresponds
to the ending points of the collective path $q^1$.
}
 \label{omega_sq}
\end{figure*}
\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
 \end{center}
\caption{Occupation numbers in each single-particle level
as a function of the collective coordinate $q^1$,
from $N=14$ to $N=24$.
The purple, green, and blue lines correspond to
$\alpha=1$, 2, and 3, respectively.
At the left end point of the collective coordinate in each panel,
the configurations correspond to the ``HF-like'' states.
See text for details.
}
 \label{occ_number}
\end{figure*}
\subsection{Non-integrable case (1): Three-level pairing model}
\label{sec:three-level-model}

@@

Next, we calculate the wave functions,
according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
The ground state corresponds to the number-projected HFB state
(variation before projection).
In contrast, the excited states are given as superposition of
generalized Slater determinants in the collective subspace,
The pair-addition transition strengths
computed using these wave functions of the excited states
are shown in Fig. \ref{3levelPad}.
For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
the ASCC+SPA method well reproduces the strengths of the exact calculation.
The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$, 
are perfectly reproduced, while
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
by about $10\%\sim20\%$.

@@

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
 \end{center}
	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
}
 \label{Pb_omega_sq}
\end{figure*}

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
 \end{center}
	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
}
 \label{Pb_occ_number}
\end{figure*}
\subsection{Non-integrable case (2): Pb isotopes}
\label{sec:Pb_isotopes}

Finally, we apply our method to neutrons' pairing dynamics in 
neutron-deficient Pb isotopes.
The spherical single-particle levels of neutrons
between the magic numbers 82 and 126 are adopted and
their energies are presented in Table \ref{Pb}. 
The coupling constant $g=0.138$ MeV is determined to reproduce
the experimental pairing gap given by the odd-even mass difference,
$\Delta(N)=\frac{(-1)^{N+1}}{2}[B(N+1)-2B(N)+B(N-1)]$ of ${}^{192}$Pb.
The even-even nuclei from ${}^{188}$Pb to ${}^{194}$Pb
are studied.
\begin{table}[htbp]
\caption{Single-particle energies of Pb isotopes used in the calculation
in units of MeV.
These are obtained from the spherical Woods-Saxon potential
with the parameters of Ref.~\cite{BM69}.
}
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
  orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
  energy(MeV)& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
\end{tabular}
\end{ruledtabular}
\label{Pb}
\end{table}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbpotential.eps}
 \end{center}
	\caption{The same as Fig. \ref{potential} but for Pb isotopes.
}
 \label{Pb_potential}
\end{figure}
The collective potentials for these isotopes are shown
in Fig. \ref{Pb_potential}.
The heights of the potentials at the left end, $V(q_L)-V(0)$,
are $2\sim3.5$ MeV.
For $^{186}$Pb, the height of the potential is not
enough to satisfy the condition, $E<V(q_L)$,
to have a closed trajectory for the first excited state
(See the last paragraph in Sec.~\ref{sec:three-level-model}).
We encounter another kind of problem for $^{196}$Pb,
which will be discussed in Sec.~\ref{sec5}.
Therefore, in this paper, we calculate the first excited states
in $^{188,190,192,194}$Pb.

\begin{table}[htbp]
\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
  \begin{ruledtabular}
\begin{tabular}{c|cccccc}
   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
\end{tabular}
\end{ruledtabular}
\label{Pb_ex}
\end{table}
We show the calculated excitation energy of the first excited state
in Table~\ref{Pb_ex}.
Experimentally, this pair vibrational excited $0^+$ state is
fragmented into several $0^+$ states due to other correlations,
such as quadrupole correlation, not taken into account in the present model.
%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
We make a comparison with the exact solution of the multi-level
pairing model.
The ASCC+SPA method quantitatively reproduces the excitation energy of
the exact solution.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
 \end{center}
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
 \end{center}
	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
}
 \label{PbPad}
\end{figure}
The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
The feature that is similar to the three-level case is observed:
dominant intraband transition and very weak interband transitions.
The accuracy from the ASCC+SPA method well reproduces
$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
and qualitatively reproduces
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ as well.
The deviation for the latter is about $25\%$.
The interband transitions are smaller than the intraband transitions
by more than two orders of magnitude.
This is also similar to the three-level model discussed
in Sec.~\ref{sec:three-level-model}.
For such weak transitions, the ASCC+SPA significantly
underestimates the strengths.
We may say that the ASCC+SPA gives reasonable results for the intraband
transitions in the realistic values of the pairing coupling constant $g$ and
single-particle levels.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
 \end{center}
	\caption{Pairing gap as a function of collective coordinate $q^1$
	in ${}^{192}$Pb. 
}
 \label{192Pb_gap}
\end{figure}
Finally, we discuss the validity of the collective model approach
assuming the pairing gap as a collective coordinate.
The 5D collective Hamiltonian assuming the quadrupole deformation
parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,$ and $0)$ as the collective coordinates
is widely utilized to analyze experimental data of quadrupole states.
Similarly, we may construct the pairing collective Hamiltonian
in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
As far as there is a one-to-one correspondence between $\Delta$ 
and the collective variable $q^1$ we obtained in the present study,
we can transform the collective Hamiltonian in $(q^1,\Phi)$
into the one in $(\Delta,\Phi)$.
The pairing gap $\Delta$ is defined as
\begin{align}
  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
\end{align}
Figure \ref{192Pb_gap} shows the pairing gap $\Delta$ in ${}^{192}$Pb
as a function of the collective coordinate $q^1$.
The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
function of $q^1$, thus no one-to-one correspondence exists.
The same behavior is observed for other Pb isotopes too.
Therefore, the pairing gap $\Delta$ is not a suitable collective coordinate
to describe the pairing dynamics in the multi-level model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Extending our former work \cite{NN18},
which demonstrated the accuracy of the SPA for the requantization
of the TDHFB dynamics in the two-level pairing model, 
we propose the ASCC+SPA method for non-integrable systems.
In this approach, we use the ASCC method to extract the 2D
collective subspace including the pair rotation.
In other words, we map the non-integrable system to an approximate
integrable system described by $(q^1,p_1;J,\Phi)$.

>>>>

\begin{abstract}
For a description of large-amplitude collective motion associated with
nuclear pairing, requantization of time-dependent mean-field dynamics
is performed using the stationary-phase approximation (SPA) to the path
integral.
We overcome the difficulty of the SPA, which is known to be applicable to integrable systems only,
by developing a requantization approach combining the SPA with the adiabatic self-consistent collective coordinate method (ASCC+SPA).
%A disadvantage of the SPA is that it is applicable only to integrable systems.
%We overcome this difficulty by developing a requantization approach
%combining the SPA with the adiabatic
%self-consistent collective coordinate method (ASCC+SPA).
We apply the ASCC+SPA to 
multi-level pairing models, which are non-integrable systems,
to study the nuclear pairing dynamics.
The ASCC+SPA gives a reasonable description of low-lying excited $0^+$
states in non-integrable pairing systems.
%\begin{description}
%\item[Background] This part would describe the
%context needed to understand what the paper
%is about.
%\item[Purpose] This part would state the purpose
%of the present paper.
%\item[Method] This part describe the methods
%used in the paper.
%\item[Results] This part would summarize the
%results.
%\item[Conclusions] This part would state the
%conclusions of the paper.
%\end{description}
\end{abstract}

@@

We study the low-lying excited $0^+$ states
in the multi-level pairing model by applying the ASCC+SPA.
The Hamiltonian of the pairing model is given in terms of
the single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{align}
	\hat{H} &= \sum_\alpha \epsilon_\alpha \hat{n}_\alpha - g \sum_{\alpha,\beta} \hat{S}_\alpha^+ \hat{S}_{\beta}^- \nonumber \\
    &= \sum_\alpha\epsilon_\alpha(2\hat{S}_\alpha^0+\Omega_\alpha) - g \hat{S}^+ \hat{S}^{-} ,
\end{align}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{\hat{S}}=\sum_\alpha \boldsymbol{\hat{S}}_\alpha$, with
\begin{eqnarray}
        \hat{S}_\alpha^0 &=& \frac{1}{2}\left(\sum_m\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha m}-\Omega_\alpha\right) ,\\
        \hat{S}_\alpha^{+} &=& \sum_{m>0}\hat{a}_{j_\alpha m}^{\dag}\hat{a}_{j_\alpha\overline{m}}^{\dag} ,
\quad   \hat{S}_\alpha^{-} = \hat{S}_\alpha^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_\alpha$ possesses $2\Omega_\alpha$-fold
degeneracy ($\Omega_\alpha=j_\alpha+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$
and $\Omega_\alpha-1/2$.
The occupation number of each level $\alpha$ is given by
$\hat{n}_\alpha = \sum_m \hat{a}^{\dag}_{j_\alpha m}\hat{a}_{j_\alpha m}
=2\hat{S}_\alpha^0+\Omega_\alpha
$.
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [\hat{S}_\alpha^0,\hat{S}_\beta^{\pm}] = \pm\delta_{\alpha\beta}\hat{S}_{\alpha}^{\pm},
\quad [\hat{S}_{\alpha}^{+},\hat{S}_{\beta}^{-}] = 2\delta_{\alpha\beta}\hat{S}_{\alpha}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is given by
$S_\alpha=\frac{1}{2}(\Omega_\alpha-\nu_\alpha)$, where $\nu_\alpha$
is the seniority
quantum number, namely the number of unpaired particles at the level $\alpha$.
In the present study, we consider only seniority-zero states with
$\nu=\sum_\alpha \nu_\alpha=0$.
The residual two-body interaction consists of the monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain the exact solutions either by solving the Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

@@

\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.45\textwidth,angle=-90]{N16X3p2trajectory.eps}
 \end{center}
\caption{Classical trajectories satisfying the EBK quantization condition
(\ref{EBK}) with $k=1$ and 2 in the $(\phi,j)$ phase space.
%The domain of phase space is $-\pi\le\phi<\pi$, $-4\le j\le4$. 
The crosses, solid and dashed lines correspond to the results
of the ASCC+SPA, TDHFB2+SPA, and TDHFB+SPA, respectively.
The crosses for the ASCC+SPA trajectories are plotted every ten calculations
($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
%For the ASCC+SPA trajectories, we plot the crosses
%every ten(?) points of the calculation,
%namely $\delta q=0.1/\sqrt{\epsilon_2-\epsilon_1}$.
}
\label{fig:N16_traj}
\end{figure}
\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2action.eps}
 \end{center}
\caption{Calculated action integrals for the $\ket{0_2^+}$ and $\ket{0_3^+}$ states as functions of time $t$.
The crosses, solid and dashed lines correspond to the ASCC+SPA,
the TDHFB2+SPA, and the TDHFB+SPA, respectively. 
%Dotted lines are the values correspond to EBK quantization condition for $\ket{0_2^+}$ and $\ket{0_3^+}$. 
The action integrals are calculated on each trajectory in Fig. \ref{fig:N16_traj}
from $(\phi,j)=(0,j_{\rm max})$ in the clockwise direction.
The crosses for the ASCC+SPA trajectories are plotted every ten calculations
($\delta q = 10dq =0.1/\sqrt{\epsilon_0}$). 
}
\label{fig:N16_tau}
\end{figure}
\begin{figure}[thb]
 \begin{center}
   \includegraphics[height=0.5\textwidth,angle=-90]{N16X3p2occ.eps}
 \end{center}
\caption{
Occupation probabilities for the $0_2^+$ and $0_3^+$ states.
The horizontal line indicates the $j=(m_2-m_1)/2$ of the quasi-spin basis
in Eq. (\ref{SPA2}).
The vertical bars at each $m_2-m_1$ from left to right
represent $|C_m|^2$ of Eq. (\ref{coef}) in
the ASCC+SPA, TDHFB2+SPA and TDHFB+SPA calculations,
respectively.
}
 \label{fig:N16_occ}
\end{figure}

@@

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
 \end{center}
 \caption{Eigenvalues of moving-frame QRPA equation as a function of
the collective coordinate $q^1$, from $N=14$ to $N=24$.
The thick (green) lines are the modes we choose as
the collective coordinate $q^1$,
while the dashed lines correspond to the zero modes ($q^n$).
In each panel, both ends of the horizontal axis corresponds
to the ending points of the collective path $q^1$.
}
 \label{omega_sq}
\end{figure*}
\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
 \end{center}
\caption{The occupation numbers $2j^{\alpha}$ in each single-particle level $\alpha$
as a function of the collective coordinate $q^1$,
from $N=14$ to $N=24$.
The purple, green, and blue lines correspond to
$\alpha=1$, 2, and 3, respectively.
At the left end point of the collective coordinate in each panel,
the configuration corresponds to the ``HF-like'' states.
See text for details.
}
 \label{occ_number}
\end{figure*}
\subsection{Non-integrable case (1): Three-level pairing model}
\label{sec:three-level-model}

@@

Next, we calculate the wave functions,
according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
The ground state corresponds to the number-projected HFB state
(variation before projection).
In contrast, the excited states are given as superposition of
generalized Slater determinants in the collective subspace,
The pair-addition transition strengths
computed using these wave functions of the excited states
are shown in Fig. \ref{3levelPad}.
For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
the ASCC+SPA method well reproduces the strengths of the exact calculation.
The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$, 
are perfectly reproduced, while
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
by about $10\%\sim20\%$.
\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=55mm,angle=-90]{Pbomega_sq.eps}
 \end{center}
	\caption{The same as Fig. \ref{omega_sq} but for Pb isotopes.
}
 \label{Pb_omega_sq}
\end{figure*}

\begin{figure*}[tb]
 \begin{center}
  \includegraphics[width=55mm,angle=-90]{Pbocc_number.eps}
 \end{center}
	\caption{The same as Fig. \ref{occ_number} but for Pb isotopes.
}
 \label{Pb_occ_number}
\end{figure*}

@@

\subsection{Non-integrable case (2): Pb isotopes}
\label{sec:Pb_isotopes}

Finally, we apply our method to neutrons' pairing dynamics in 
neutron-deficient Pb isotopes.
The spherical single-particle levels of neutrons
between the magic numbers 82 and 126 are adopted and
their energies are presented in Table \ref{Pb}. 
The coupling constant $g=0.138$ MeV is determined to reproduce
the experimental pairing gap given by the odd-even mass difference,
$\Delta(N)=\frac{(-1)^{N+1}}{2}[B(N+1)-2B(N)+B(N-1)]$ of ${}^{192}$Pb.
The even-even nuclei from ${}^{188}$Pb to ${}^{194}$Pb
are studied.
\begin{table}[tb]
\caption{Single-particle energies of Pb isotopes used in the calculation
in units of MeV.
These are obtained from the spherical Woods-Saxon potential
with the parameters of Ref.~\cite{BM69}.
}
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
  orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
  energy(MeV)& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
\end{tabular}
\end{ruledtabular}
\label{Pb}
\end{table}

@@

\begin{figure}[bt]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbpotential.eps}
 \end{center}
	\caption{The same as Fig. \ref{potential} but for Pb isotopes.
}
 \label{Pb_potential}
\end{figure}
The collective potentials for these isotopes are shown
in Fig. \ref{Pb_potential}.
The heights of the potentials at the left end, $V(q_L)-V(0)$,
are $2\sim3.5$ MeV.
For $^{186}$Pb, the height of the potential is not
enough to satisfy the condition, $E<V(q_L)$,
to have a closed trajectory for the first excited state
(See the last paragraph in Sec.~\ref{sec:three-level-model}).
We encounter another kind of problem for $^{196}$Pb,
which will be discussed in Sec.~\ref{sec5}.
Therefore, in this paper, we calculate the first excited states
in $^{188,190,192,194}$Pb.

We show the calculated excitation energy of the first excited state
in Table~\ref{Pb_ex}.
Experimentally, this pair vibrational excited $0^+$ state is
fragmented into several $0^+$ states due to other correlations,
such as quadrupole correlation, not taken into account in the present model.
%The value is nothing to do with experimental value because pairing model is too simple to describe realistic nuclear interaction. 
We make a comparison with the exact solution of the multi-level
pairing model.
The ASCC+SPA method quantitatively reproduces the excitation energy of
the exact solution.

\begin{table}[bt]
\caption{The same as Table \ref{ex} but for Pb isotopes. The energies are given in units of MeV.}
  \begin{ruledtabular}
\begin{tabular}{c|cccccc}
   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
ASCC+SPA & $-$ & $2.31$ & $2.21$ & $2.12$ & $2.04$ & $-$ \\ 
Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$
\end{tabular}
\end{ruledtabular}
\label{Pb_ex}
\end{table}
\begin{figure}[htb]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbintra_trans.eps}
 \end{center}
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{Pbinter_trans.eps}
 \end{center}
	\caption{The same as Fig. \ref{3levelPad} but for Pb isotopes.
}
 \label{PbPad}
\end{figure}
The pair-addition transition strengths are shown in Fig. \ref{PbPad}.
The feature that is similar to the three-level case is observed:
dominant intraband transition and very weak interband transitions.
The accuracy from the ASCC+SPA method well reproduces
$B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
and qualitatively reproduces
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ as well.
The deviation for the latter is about $25\%$.
The interband transitions are smaller than the intraband transitions
by more than two orders of magnitude.
This is also similar to the three-level model discussed
in Sec.~\ref{sec:three-level-model}.
For such weak transitions, the ASCC+SPA significantly
underestimates the strengths.
We may say that the ASCC+SPA gives reasonable results for the intraband
transitions in the realistic values of the pairing coupling constant $g$ and
single-particle levels.

Finally, we discuss the validity of the collective model approach
assuming the pairing gap as a collective coordinate.
The 5D collective Hamiltonian assuming the quadrupole deformation
parameters $\alpha_{2\mu} (\mu=\pm2,\pm1,$ and $0)$ as the collective coordinates
is widely utilized to analyze experimental data of quadrupole states.
Similarly, we may construct the pairing collective Hamiltonian
in terms of the pairing gap $\Delta$ and the gauge angle $\Phi$. 
As far as there is a one-to-one correspondence between $\Delta$ 
and the collective variable $q^1$ we obtained in the present study,
we can transform the collective Hamiltonian in $(q^1,\Phi)$
into the one in $(\Delta,\Phi)$.
The pairing gap $\Delta$ is defined as
\begin{align}
  \Delta (q) &\equiv \left. g\braket{\Phi,J;q,p|\hat{S}^-|\Phi,J;q,p} \right|_{\Phi=p=0} \nonumber \\
  &= g\sum_\alpha \sqrt{j^\alpha(\Omega_\alpha-j^\alpha)} .
\end{align}
Figure \ref{192Pb_gap} shows the pairing gap $\Delta$ in ${}^{192}$Pb
as a function of the collective coordinate $q^1$.
The peak in $\Delta$ is near $q^1=0$ and it is not a monotonic
function of $q^1$, thus no one-to-one correspondence exists.
The same behavior is observed for other Pb isotopes too.
Therefore, the pairing gap $\Delta$ is not a suitable collective coordinate
to describe the pairing dynamics in the multi-level model.

@@

\begin{figure}[t]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{192Pbgap.eps}
 \end{center}
	\caption{Pairing gap as a function of collective coordinate $q^1$
	in ${}^{192}$Pb. 
}
 \label{192Pb_gap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Extending our former work \cite{NN18},
which demonstrated the accuracy of the SPA for the requantization
of the TDHFB dynamics in the two-level pairing model, 
we propose the ASCC+SPA method for non-integrable systems.
In this approach, we use the ASCC method to extract the 2D
collective subspace including the pair rotation.
In other words, we extract an approximate integrable system 
in the non-integrable system described by $(q^1,p_1;J,\Phi)$.
